Disparate views of disparity

### 2017-11-01 Analysis/disparity_methods.Rmd
methods update

@@

```{r}
## Reading the data
data_raw <- read.csv("../Data/disparity_methods.csv", stringsAsFactors = FALSE)

@@

>>>>

Additionally I collected the number of matches per year for the terms "morphological disparity" both in the text (fuzzy matching) or in the title (exact matching).

@@

```{r}
## Reading the data
data_raw <- read.csv("../Data/disparity_methods.csv", stringsAsFactors = FALSE)
search_results <- read.csv("../Data/GoogleSearch_occurences.csv", stringsAsFactors = FALSE)

@@

# Occurence of morphological disparity papers

```{r}
disparity_fuzzy <- search_results[-c(1:2, 60:65),3]
disparity_exact <- search_results[-c(1:2, 60:65),2]

## Number of papers
plot(seq(from = 1960, to = 2016), rev(disparity_fuzzy)/max(disparity_fuzzy), type = "l", xlab = "", ylab = "Proportion of papers")
lines(seq(from = 1960, to = 2016), rev(disparity_exact)/max(disparity_exact), type = "l", col = "grey")
```
